Updates on the Exoplanet Orbit Database

### 2014-02-12 draft/ms.tex
Typo fix and note on KDE.
Structure changed

\textit {Sharon: you need to say what KOI stores. When writing each
  field, keep in mind you need to cover the following so that the
  reader will completely understand: (1) what the field stands for
  (e.g., in case of an abbreviation like KOI); (2) what the field
  physically means, like `KOI' means planet candidates that have transit
  signals as detected by \kepler\ but have not been confirmed, and
  make sure to be thorough at what you say -- sometimes things are not
  that obvious to an outsider reader, e.g., think if a cosmologist
  would understand what you're saying when reading it; (3) what the
  field actually contains, e.g. KOI contains the KOI number designated
  by the \kepler\ team (right?), it is a floating point number, and
  sometimes maybe even worth giving an example, e.g. KOI 30.1 or
  something...; (4) why we added this new field, if this information
  is helpful, or if it's a revised field since \cite{Wright2011}, what
  is changed. Also, use \keper\ (which is a defined symbol in our ms.tex file),
  instead of typing out Kepler, since you need italic.
  Don't be afraid to write more! Being concise is important, but it's
  always easier to trim down things than to add things on, especially
  for a documentation type of paper like this. Let's be thorough at
  first, then try to reach optimal conciseness.}

@@

%------------------------------------------------------------------------------
\subsection{Stellar Parameters}
Stellar parameters section is consisted of 3 parts: Stellar properties, Stellar magnitudes, and Coordinates and Catalog. This section is to provide our users detailed information about the exoplanet hosting stars. Stellar properties section contains name, mass, and consistent set of metalicities (FE) , effective temperature (TEFF), surface gravity (LOGG), projected rotational velocity (VSINI), and the systematic radial velocity (GAMMA). Stellar magnitudes section includes optical magnitudes of the star (V and BMV) as well as 2MASS infrared (J, H, and K) and Kepler bandpass magnitude (KP). Coordinates and Catalog section includes the right ascension (RA) and the declination (DEC) of the host star, parallax (PAR) and distance (DIST) and the integers designated by different catalogs.

DIST is the distance of the host star in the unit of pc. It sometimes is calculated from the parallax that come from the Hipparcos data set by van Leeuwen (200).

ZZZ KP added?

@@

%------------------------------------------------------------------------------
\subsection{Stellar Properties}

Difference from Stellar Parameters: these are derived parameters based
on spectroscopy and stellar models.
Added fields since \cite{Wright2011}:

RSTAR

RHOSTAR

@@

>>>>

@@

@@

%------------------------------------------------------------------------------

\subsection{Stellar Properties}
ZZZ Stellar parameters and stellar properties have been merged.

Stellar parameters section is consisted of 3 parts: Stellar properties, Stellar magnitudes, and Coordinates and Catalog. This section is to provide our users detailed information about the exoplanet hosting stars. Stellar properties section contains name, mass, and consistent set of metalicities (FE) , effective temperature (TEFF), surface gravity (LOGG), projected rotational velocity (VSINI), and the systematic radial velocity (GAMMA). Stellar magnitudes section includes optical magnitudes of the star (V and BMV) as well as 2MASS infrared (J, H, and K) and Kepler bandpass magnitude (KP). Coordinates and Catalog section includes the right ascension (RA) and the declination (DEC) of the host star, parallax (PAR) and distance (DIST) and the integers designated by different catalogs.

Difference from Stellar Parameters: these are derived parameters based
on spectroscopy and stellar models. 
==>> Not always true for RSTAR because some literatures give the value. 
Added fields since \cite{Wright2011}:

RSTAR is the radius of the star in the solar radius.

RHOSTAR is the density of the star in the unit of $g/cm^3$

%------------------------------------------------------------------------------
\subsection {Stellar Magnitudes}

@@

%------------------------------------------------------------------------------
\subsection{Coordinates and Catalogs}

DIST is the distance of the host star in the unit of pc. It sometimes is calculated from the parallax that come from the Hipparcos data set by van Leeuwen (2009).
